Descriptive Analysis

### 2020-05-18 code/analysis.Rmd
Update analysis.Rmd

q01
```

@@

@@

# Save Results
```{r}
block2 <- list(q01 = q01, 
                    q02 = q02, 
                    q03 = q03, 
                    q04 = q04, 
                    q05 = q05,
               prereg_data = prereg_where_data)

@@

# Question Block 3: Teaching Coverage, Attitudes
```{r}
# global
n_participants <- nrow(wide_all)
```

@@

q_rc_t.spec.share <- q_rc_t.spec %>% 
  group_by(lecture) %>% summarise(n = n()) %>% ungroup() %>% 
  mutate(share = n / n_participants * 100) %>% arrange(share %>% desc())
```

@@

## Block 3
```{r}
block3 <- list(qrps_teaching = q_qrp_t.spec,
               qrps_teaching_share = q_qrp_t.spec_share,
               rc_teaching_general = rc_teaching_general,
               rc_teaching_unis = rc_teaching_unis.out,
               rc_teaching_specific = q_rc_t.spec,
               rc_teaching_specific_share = q_rc_t.spec.share,
               nosi_data = nosi_agg2,
               nosi_events = nosi_events
               )

>>>>

q01

# changed, 05.03.2020: Because we can not be sure, if the answers to "project" and "other refer to single projects or mutiple projects, we calculate a second number which excludes these projects from the calculation.

q01.reduced <- long %>% 
  filter(project %in% c('emp.intern', 'thesis.bsc', 'thesis.msc')) %>% 
  # number of applied practices (per individual and type of project)
  group_by(id, type_of_practice, n_projects) %>% 
  summarise(applied_practices = sum(rp_applied, na.rm = TRUE)) %>% 
  ungroup() %>% 
  mutate(practices_per_project = applied_practices / n_projects) %>%

q01.reduced
```

@@

### Comparison: Share of one-time application vs. share of projects with practices
Added (28.04.2020)

It obviously makes a difference, whether you ask "did you apply this practice at least once in any project?" or "did you apply this practice in this specific project?". Here, we calculate the difference.

```{r}
share_comparison <- q05 %>% 
  ungroup() %>% 
  rename(share_projects = share) %>% 
  arrange(practice) %>% 
  mutate(share_once = q03 %>% arrange(practice) %>% pull(share)) %>% 
  arrange(desc(share_projects)) %>% 
  # filter(type_of_practice == "Questionable") %>% 
  mutate(diff = share_once - share_projects)

share_comparison_agg <- share_comparison %>% 
  group_by(type_of_practice) %>% 
  summarise(mean_diff = mean(diff),
            mean_project = mean(share_projects),
            mean_once = mean(share_once))

share_comparison
share_comparison_agg
```

@@

# Save Results
```{r}
block2 <- list(q01 = q01, 
               q01.reduced = q01.reduced,
                    q02 = q02, 
                    q03 = q03, 
                    q04 = q04, 
                    q05 = q05,
               share_comparison = share_comparison,
               share_comparison_agg = share_comparison_agg,
               prereg_data = prereg_where_data)

@@

# Question Block 3: Teaching Coverage, Attitudes
```{r}
# global
n_participants <- nrow(wide_all)
n_bsc <- wide_all %>% filter(study_stage_mc == "Bachelor") %>% nrow()
n_msc <- wide_all %>% filter(study_stage_mc == "Master") %>% nrow()
```

@@

dgps_mandatory_lectures = c("General Psychology", "Introductory Class", "Methods, Stats, Expra", "General Psychology", "Social Psychology", "Developmental Psychology", "Differential Psychology", "Biological- / Neuropsychology", "Diagnostics")

q_rc_t.spec.share <- q_rc_t.spec %>% 
  group_by(lecture) %>% summarise(n = n()) %>% ungroup() %>% 
  mutate(share = n / n_msc * 100) %>% arrange(share %>% desc())

q_rc_t.spec.share.msc <- q_rc_t.spec %>% 
  filter(study_stage_mc == "Master") %>% 
  filter(lecture %in% dgps_mandatory_lectures) %>% 
  group_by(lecture) %>% summarise(n = n()) %>% ungroup() %>% 
  mutate(share = n / n_msc * 100) %>% arrange(share %>% desc())

q_rc_t.spec.share.bsc <- q_rc_t.spec %>% 
  filter(study_stage_mc == "Bachelor") %>% 
  group_by(lecture) %>% summarise(n = n()) %>% ungroup() %>% 
  mutate(share = n / n_bsc * 100) %>% arrange(share %>% desc())
```

@@

## Block 3
```{r}
block3 <- list(qrps_teaching = q_qrp_t.spec,
               qrps_teaching_share = q_qrp_t.spec_share,
               rc_teaching_general = rc_teaching_general,
               rc_teaching_unis = rc_teaching_unis.out,
               rc_teaching_specific = q_rc_t.spec,
               rc_teaching_specific_share = q_rc_t.spec.share,
               rc_teaching_specific_share_bsc = q_rc_t.spec.share.bsc,
               rc_teaching_specific_share_msc = q_rc_t.spec.share.msc,
               nosi_data = nosi_agg2,
               nosi_events = nosi_events
               )
